Hydra Battles and Cie

### 2021-07-20 doc/chapter-primrec.tex
Insert some new snippets extracted from the code.
more snippets

\index{primrec}{Types!naryFunc}
\begin{Coqsrc}
Fixpoint naryFunc (n : nat) : Set :=
  match n with
  | O => nat
  | S n => nat -> naryFunc n
  end.
\end{Coqsrc}

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}}.
\begin{Coqsrc}
Require Import primRec.
Import extEqualNat.

Compute naryFunc 3.
\end{Coqsrc}

\begin{Coqanswer}
= nat -> nat -> nat -> nat
  : Set  
\end{Coqanswer}

\begin{Coqsrc}
Check plus: naryFunc 2.

Check 42: naryFunc 0.

Check (fun n p q : nat =>  n * p + q): naryFunc 3.
\end{Coqsrc}

@@

\begin{Coqsrc}
Compute naryRel 2.
\end{Coqsrc}

\begin{Coqanswer}
 = nat -> nat -> bool
     : Set
\end{Coqanswer}

@@

\begin{Coqsrc}
Compute extEqual 2.
\end{Coqsrc}

\begin{Coqanswer}
     = fun a b : naryFunc 2 => forall x x0 : nat, a x x0 = b x x0
     : naryFunc 2 -> naryFunc 2 -> Prop
 \end{Coqanswer}

\begin{Coqsrc}
Example extEqual_ex1 : extEqual 2 mult (fun x y =>  y * x + x - x) .
Proof.
  intros x y.
\end{Coqsrc}

\begin{Coqanswer}
  x, y : nat
  ============================
  extEqual 0 (x * y) (y * x)
\end{Coqanswer}

\begin{Coqanswer}
1 subgoal (ID 10)

  x, y : nat
  ============================
  x * y = y * x + x - x
\end{Coqanswer}

\begin{Coqsrc}
  rewrite <- Nat.add_sub_assoc, Nat.sub_diag.
  - ring.
  - apply le_n.  
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Search (is_PR 2 (fun _ _ => nat_rec _ _ _ _)).
\end{Coqsrc}

\begin{Coqanswer}
ind1ParamIsPR:
  forall f : nat -> nat -> nat -> nat,
  isPR 3 f ->
  forall g : nat -> nat,
  isPR 1 g ->
  isPR 2
    (fun a b : nat =>
     nat_rec (fun _ : nat => nat)
                 (g b) (fun x y : nat => f x y b) a)
\end{Coqanswer}

>>>>

\index{primrec}{Types!naryFunc}
\input{movies/snippets/extEqualNat/naryFunc.tex}

@@

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}}.

\input{movies/snippets/PrimRecExamples/naryFunc3}
\input{movies/snippets/PrimRecExamples/checknaryFunc}

@@

\input{movies/snippets/PrimRecExamples/naryRel2}

@@

\input{movies/snippets/PrimRecExamples/extEqual2a}

  Getting rid of the term \texttt{x-x}, we generate two easy-to-solve sub-goals.

\vspace{6pt}
\noindent
\input{movies/snippets/PrimRecExamples/extEqual2b}

@@

\input{movies/snippets/PrimRecExamples/PrimRecExamplesSearch}
